XRONOS: An Open Data Infrastructure for Archaeological Chronology

### 2024-12-05 paper.tex
Save figures in figures/

\begingroup
\fontsize{9.8pt}{11.7pt}\selectfont

\begin{longtable}{>{\raggedright\arraybackslash}p{\dimexpr 0.40\linewidth -2\tabcolsep-1.5\arrayrulewidth}>{\raggedleft\arraybackslash}p{\dimexpr 0.15\linewidth -2\tabcolsep-1.5\arrayrulewidth}>{\raggedleft\arraybackslash}p{\dimexpr 0.15\linewidth -2\tabcolsep-1.5\arrayrulewidth}>{\raggedright\arraybackslash}p{\dimexpr 0.30\linewidth -2\tabcolsep-1.5\arrayrulewidth}}

@@

\tabularnewline

@@

\end{longtable}

\endgroup

@@

\pandocbounded{\includegraphics[keepaspectratio]{paper_files/figure-pdf/fig-c14-datasets-time-1.pdf}}

@@

\pandocbounded{\includegraphics[keepaspectratio]{paper_files/figure-pdf/fig-c14-datasets-map-1.pdf}}

@@

\pandocbounded{\includegraphics[keepaspectratio]{paper_files/figure-pdf/fig-c14-global-1.pdf}}

@@

\pandocbounded{\includegraphics[keepaspectratio]{paper_files/figure-pdf/fig-data-model-1.pdf}}

>>>>

@@

\fontsize{9.8pt}{11.7pt}\selectfont
\begin{tabular*}{\linewidth}{@{\extracolsep{\fill}}>{\raggedright\arraybackslash}p{\dimexpr 0.40\linewidth -2\tabcolsep-1.5\arrayrulewidth}>{\raggedleft\arraybackslash}p{\dimexpr 0.15\linewidth -2\tabcolsep-1.5\arrayrulewidth}>{\raggedleft\arraybackslash}p{\dimexpr 0.15\linewidth -2\tabcolsep-1.5\arrayrulewidth}>{\raggedright\arraybackslash}p{\dimexpr 0.30\linewidth -2\tabcolsep-1.5\arrayrulewidth}}

@@

\end{tabular*}

@@

\pandocbounded{\includegraphics[keepaspectratio]{figures/fig-c14-datasets-time-1.pdf}}

@@

\pandocbounded{\includegraphics[keepaspectratio]{figures/fig-c14-datasets-map-1.pdf}}

@@

\pandocbounded{\includegraphics[keepaspectratio]{figures/fig-c14-global-1.pdf}}

@@

\pandocbounded{\includegraphics[keepaspectratio]{figures/fig-data-model-1.pdf}}
